I am very grateful to my advisor Prof. Chuan-Ming Liu for providing me with continuous support and guidance throughout my PhD program which has been immensely helpful to me. My parents and sister provided the emotional support needed to take up this challenge and complete it successfully. Akbar and Nick - without your support this journey would not have been possible.

I want to thank Prof. Ya-Hui Chang, Prof. Jen-Yeu Chen, Prof. Kuan-Chou Lai, Prof. Prof. Li-Chun Wang, and Prof. Chang-Wu Yu for serving on my committee to provide their guidance on improving this dissertation. I am also indebted to a number of other professors from whom I gained immensely valuable knowledge over the course of the past five years.

I am thankful to the Department of Computer Science and Information Engineering, the College of Electrical Engineering and Computer Science, the Graduate School of National Taipei University of Technology, and the Ministry of Science of Technology for providing the needed financial support. The research work carried out in this dissertation would not have been possible without the financial support from these institutions and organizations. The opportunities provided by the  Department of Computer Science and Information Engineering to work as a teaching assistance not only supported me financially but also provided a valuable experience that would benefit me in the future.

I am grateful and fortunate to have a number of close, supportive, and entertaining friends who made this journey enjoyable and memorable. Doris, Henry, Ian, Paul, Sky, Stanley, and Winny - thank you for giving me the most memorable and awesome years of my life.